R for Clinical Study Reports and Submission

### 2023-01-15 project-folder.Rmd
Fix broken URLs reported by URL checker

For R users, you already benefit from a well-defined and consistent folder structure.
That is the [R package folder structure](https://github.com/rstudio/cheatsheets/raw/master/package-development.pdf).
Every R package developer is required to follow the same convention to organize
their R functions before the R package can be disseminated through the Comprehensive R Archive Network (CRAN).
As a user, you can easily install and use those R packages after downloading from CRAN.
There are many good resources to guide developers on R package development,
such as, the [R Packages book](https://r-pkgs.org/) by Hadley Wickham.

@@

::: {.rmdnote data-latex=""}
This is the same level of reproducibility in most SAS environments:
<https://support.sas.com/techsup/pcn/altopsys.html>
:::

@@

# set up repository based on the snapshot date
repos <- paste0("https://mran.microsoft.com/snapshot/", snapshot)

@@

```
Current project R package repository:
    https://mran.microsoft.com/snapshot/2021-08-06
```

>>>>

For R users, you already benefit from a well-defined and consistent folder structure.
That is the [R package folder structure](https://github.com/rstudio/cheatsheets/blob/main/package-development.pdf).
Every R package developer is required to follow the same convention to organize
their R functions before the R package can be disseminated through the Comprehensive R Archive Network (CRAN).
As a user, you can easily install and use those R packages after downloading from CRAN.
There are many good resources to guide developers on R package development,
such as, the [R Packages book](https://r-pkgs.org/) by Hadley Wickham.

@@

::: {.rmdnote data-latex=""}
This is the same level of reproducibility in most SAS environments:
<https://support.sas.com/en/technical-support/services-policies.html#altos>
:::

@@

# set up repository based on the snapshot date
repos <- paste0("https://mran.microsoft.com/snapshot/", snapshot, "/")

@@

```
Current project R package repository:
    https://mran.microsoft.com/snapshot/2021-08-06/
```

### 2023-01-15 slides/china-r.Rmd
Fix broken URLs reported by URL checker

- [FDA: Statistical Software Clarifying Statement](https://www.fda.gov/files/about%20fda/published/Statistical-Software-Clarifying-Statement-PDF.pdf)

@@

We share the same philosophy described in
[Section 1.1 of R Packages book](https://r-pkgs.org/intro.html#intro-phil) and quote here.

@@

Training: [December 6th, Deming Conference 2021](https://demingconference.org/programs/2021-program/)

@@

- Contact us for R developer or Methodology Research Positions:
  - Yilong Zhang: <https://elong0527.github.io/>
  - Nan Xiao: <https://nanx.me/>
  - Keaven Anderson: <https://www.linkedin.com/in/keaven-anderson-09aa7538/>

>>>>

- [FDA: Statistical Software Clarifying Statement](https://www.fda.gov/media/161196/download)

@@

We share the same philosophy described in
[Section 1.1 of the R Packages book](https://r-pkgs.org/introduction.html#intro-phil) and quote here.

@@

Training: [December 6th, Deming Conference 2021](https://demingconference.org/wp-content/uploads/2021/07/2021-Deming-Conference-Printed-Program-v1.0.pdf)

@@

- Contact us for R developer or Methodology Research Positions:
  - Yilong Zhang: <https://elong0527.github.io/>
  - Nan Xiao: <https://nanx.me/>
  - Keaven Anderson: <https://keaven.github.io/>

### 2023-01-15 slides/r4csr-gwu.Rmd
Fix broken URLs reported by URL checker

- R is widely used in visualization
  - [SafetyGraphics](https://github.com/SafetyGraphics/safetyGraphics)
  - [forestly](https://elong0527.github.io/forestly/articles/example.html#construct-interactive-forest-plot-1): [Interactive forest plot for DMC safety monitoring in clinical trials](https://rinpharma.com/publication/rinpharma_194/)

>>>>

- R is widely used in visualization
  - [SafetyGraphics](https://github.com/SafetyGraphics/safetyGraphics)
  - [forestly](https://elong0527.github.io/forestly/articles/forestly.html): [Interactive forest plot for DMC safety monitoring in clinical trials](https://rinpharma.com/publication/rinpharma_206/)

### 2023-01-15 slides/r4csr-psi.Rmd
Fix broken URLs reported by URL checker

- R is widely used in visualization
  - [metalite.table1](https://elong0527.github.io/metalite.table1/articles/metalite-table1.html): Interactive demographic table.
  - [forestly](https://elong0527.github.io/forestly/articles/example.html#construct-interactive-forest-plot-1): [Interactive forest plot for DMC safety monitoring in clinical trials](https://rinpharma.com/publication/rinpharma_194/)

>>>>

- R is widely used in visualization
  - [metalite.table1](https://elong0527.github.io/metalite.table1/articles/metalite-table1.html): Interactive demographic table.
  - [forestly](https://elong0527.github.io/forestly/articles/example.html#construct-interactive-forest-plot-1): [Interactive forest plot for DMC safety monitoring in clinical trials](https://rinpharma.com/publication/rinpharma_206/)

### 2023-01-15 slides/workshop-slides.Rmd
Fix broken URLs reported by URL checker

- [R Consortium](https://www.r-consortium.org/projects/isc-working-groups)
  - R validation hub
  - Submission working group
  - R Tables for Regulatory Submission (RTRS) working group
  - Please consider to join and contribute to a working group.

@@

- Public available CDISC pilot [study data located at CDISC Bitbucket repository](https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets).

@@

<https://r4csr.org/efficacy.html>

>>>>

- [R Consortium](https://www.r-consortium.org/all-projects/isc-working-groups)
  - R validation hub
  - Submission working group
  - R Tables for Regulatory Submission (RTRS) working group
  - Please consider to join and contribute to a working group.

@@

- Public available CDISC pilot [study data located at CDISC GitHub repository](https://github.com/cdisc-org/sdtm-adam-pilot-project/tree/master/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets).

@@

<https://r4csr.org/efficacy-table.html>
